Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
review Synthesis Process using DSVerifier

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ [eq.  \ref{FWL_tf}] (step B) to
calulate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

@@

To exploit the present approach full potential, a dynamical plant that can
present physical components must be considered.  However, a discrete plant
model can also demonstrate some benefits of the present approach, which
considers FWL effects in the digital controller implementation.  In
particular, a classical cruise control example is extracted from the
literature~\cite{Astrom08}, where the discrete plant model (with time step
of $0.2$s) is represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}

>>>>

Given a model $(\hat{C}(z),\hat{G}(z), \mathbb{R}\langle I,F \rangle)$,
provided in an ANSI-C code input file (Steps 1-5), DSVerifier constructs a
non-deterministic model to represent the plant family $\mathfrak{G}(z)$
(Step A), and a transfer function $f$ represented by Eq.~\ref{FWL_tf} (step B) to
calculate the implementation $f(\hat{C}(z)) \rightarrow \tilde C(z)$ of the
controller (step C).  Finally DSVerifier builds an intermediate ANSI-C code
for the digital system implementation, which is used as input for the
model-checker (Step D).

@@

In order to exploit the present approach full potential, a dynamical plant that can
present physical components must be considered.  However, a discrete plant
model can also demonstrate some benefits of the present approach, which
considers FWL effects in the digital controller implementation.  In
particular, a classical cruise control example is extracted from the
literature~\cite{Astrom08}, where the discrete plant model (with time step
of $0.2$s) is represented by the following z-expression:
%
\begin{equation}
\label{Eq:running-example-plant}
G\left(z\right) := \frac{0.0264}{z-0.9998}.
\end{equation}
